Efficient Computation of Extended Sources

### 2021-07-13 repro/papers/sseprecond/paper.tex
updated paper.tex and project/SConstruct as transmitted to Mohamed

\plot{compreshh0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  homogeneous model, point source (Figure \ref{fig:recphh0}), inversion 
  in homogeneous model. Penalty weight
  $\alpha=0$.}

@@

@@

\plot{compresll0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  lens model, point source (Figure \ref{fig:recplh0}), inversion 
  in lens model. Penalty weight
  $\alpha=0$.}

\plot{compnreshh0}{width=\textwidth}{Comparison of normal residual
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted
  vs. iteration. Data = homogeneous model, point source (Figure
  \ref{fig:recphh0}), inversion in homogenous model. Penalty weight $\alpha=0$.}

@@

@@

\plot{compnresll0}{width=\textwidth}{Comparison of normal residual 
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted 
  vs. iteration. Data = lens model, point source (Figure 
  \ref{fig:recplh0}), inversion in lens model. Penalty weight
  $\alpha=0$.}

>>>>

\plot{compres0hh0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  homogeneous model, point source (Figure \ref{fig:recphh0}), inversion 
  in homogeneous model. Penalty weight
  $\alpha=0$.}

@@

\plot{compres0ll0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  lens model, point source (Figure \ref{fig:recplh0}), inversion 
  in lens model. Penalty weight 
  $\alpha=0$.}

\plot{compres1hh0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  homogeneous model, point source (Figure \ref{fig:recphh0}), inversion 
  in homogenous model. Penalty weight 
  $\alpha=10^{-3}$.}

@@

\plot{compres1ll0}{width=\textwidth}{Comparison of residual Euclidean 
  norms: CG (blue), PCG (red), plotted vs. iteration. Data =
  lens model, point source (Figure \ref{fig:recplh0}), inversion 
  in lens model. Penalty weight
  $\alpha=0$.}

\plot{compnres0hh0}{width=\textwidth}{Comparison of normal residual
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted
  vs. iteration. Data = homogeneous model, point source (Figure
  \ref{fig:recphh0}), inversion in homogenous model. Penalty weight $\alpha=0$.}

@@

\plot{compnres0ll0}{width=\textwidth}{Comparison of normal residual 
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted 
  vs. iteration. Data = lens model, point source (Figure 
  \ref{fig:recplh0}), inversion in lens model. Penalty weight 
  $\alpha=0$.}

\plot{compnres1hh0}{width=\textwidth}{Comparison of normal residual 
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted 
  vs. iteration. Data = homogeneous model, point source (Figure 
  \ref{fig:recphh0}), inversion in homogenous model. Penalty weight 
  $\alpha=10^{-3}$.}

@@

\plot{compnres1ll0}{width=\textwidth}{Comparison of normal residual 
  (gradient) Euclidean norms: CG (blue), PCG (red), plotted 
  vs. iteration. Data = lens model, point source (Figure 
  \ref{fig:recplh0}), inversion in lens model. Penalty weight
  $\alpha=10^{-3}$.}
